Hydras \& Co.

### 2022-05-14 doc/hydra-chapter.tex
revision book (-> p. 32)

\begin{exercise}
It happens very often that, in the proof of  a proposition of the form 
(\texttt{$\forall\,$ h:Hydra, $P$ h}), the predicate \texttt{P0}
is  (\texttt{h\_forall $P$}).  Design a tactic for induction on hydras that frees the user from binding explicitly \texttt{P0},  and solves trivial subgoals. Apply it for writing  a shorter proof of \texttt{height\_lt\_size}.
\end{exercise}

@@

If Hercules chops off a head near the floor, there is no replication at all. We use an auxiliary 
predicate \texttt{S0}, associated with the removing of one head from a sequence of hydras.

@@

We combine the two cases above into a single relation.
First,  we define the  relation \texttt{(round\_n n h h')} where \texttt{n} is the expected number of  replications (irrelevant in the case of an \texttt{R1}-transformation).

@@

\index{hydras}{Library Hydra!Predicates!round\_n}

\input{movies/snippets/Hydra_Definitions/roundNDef}

By abstraction over \texttt{n}, we define a \emph{round} (small step) of a battle:

\index{hydras}{Library Hydra!Predicates!round}
\label{sect:infix-round}

\input{movies/snippets/Hydra_Definitions/roundDef}

@@

\begin{itemize}
\item For proving $\forall y, x\,R^+\,y \;\arrow\; P\,y$, prefer 
\texttt{clos\_trans\_n1}
\item For proving $\forall x,\,x\,R^+\,y \;\arrow\; P\,x$, prefer \texttt{clos\_trans\_1n}
\item For proving $\forall x\,y, \,x\,R^+\,y \;\arrow\;P\,x\,y$,  
prefer \texttt{clos\_trans},
\end{itemize}
But there is no ``wrong choice'' at all: the equivalence lemmas in \linebreak 
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Relations.Operators_Properties.html}{Coq.Relations.Operators\_Properties} 
 allow the user
to convert any one of the three closures into another one before applying the corresponding elimination tactic.
The same remark also holds for reflexive and transitive closures. 
\end{remark}

@@

\begin{exercise}[Interactive battles]
\label{exo:interactive-battle}
Given a hydra \texttt{h}, the specification of a hydra battle for \texttt{h} is the type 
\Verb@{h':Hydra | h -*-> h'}@. In order to avoid long sequences of \texttt{split}, \texttt{left}, and 
\texttt{right}, design a set of dedicated tactics for the interactive building of a battle.
Your tactics will have the following functionalities:
\begin{itemize}
\item  Chose to stop a battle, or continue
\item Chose an expected number of replications
\item Navigate in a hydra, looking for a head to chop off.
\end{itemize}

@@

The most general class of battles is \texttt{free}, which allows the hydra to chose any replication factor at every step:

>>>>

\begin{exercise}
It happens very often that, in the proof of  a proposition of the form 
(\texttt{$\forall\,$ h:Hydra, $P$ h}), the predicate \texttt{P0}
is  (\texttt{h\_forall $P$}).  Design a tactic for induction on hydras that frees the user from binding explicitly \texttt{P0},  and solves trivial subgoals. Apply it for writing  a shorter proof script of \texttt{height\_lt\_size}.
\end{exercise}

@@

If Hercules chops off a head close to the root, there is no replication at all. We use an auxiliary 
predicate \texttt{S0}, associated with the removing of one head from a sequence of hydras.

@@

Let us merge \texttt{R1} and \texttt{R1}  into a single relation.
First,  we define the  relation \texttt{(round\_n n h h')} where \texttt{n} is the expected number of  replications (irrelevant in the case of an \texttt{R1}-transformation).
Then, we define a \emph{round} (small step) of a battle
by abstraction over \texttt{n},

@@

\index{hydras}{Library Hydra!Predicates!round\_n}
\index{hydras}{Library Hydra!Predicates!round}
\label{sect:infix-round}

\inputsnippets{Hydra_Definitions/roundNDef, Hydra_Definitions/roundDef}

@@

\begin{itemize}
\item To prove $\forall y, x\,R^+\,y \;\arrow\; P\,y$, prefer 
\texttt{clos\_trans\_n1}
\item To prove proving $\forall x,\,x\,R^+\,y \;\arrow\; P\,x$, prefer \texttt{clos\_trans\_1n}
\item To prove $\forall x\,y, \,x\,R^+\,y \;\arrow\;P\,x\,y$,  
prefer \texttt{clos\_trans},
\end{itemize}
But there is no ``wrong choice'' at all: the equivalence lemmas in \linebreak 
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Relations.Operators_Properties.html}{Coq.Relations.Operators\_Properties} 
 allow the user
to convert any one of the three closures into another one before applying the corresponding elimination tactic.
The same remark also holds for reflexive and transitive closures. 
\end{remark}

@@

\begin{exercise}[Interactive battles]
\label{exo:interactive-battle}
Given a hydra \texttt{h}, the specification of a hydra battle for \texttt{h} is the type 
\Verb@{h':Hydra | h -*-> h'}@. In order to avoid long sequences of \texttt{split}, \texttt{left}, and 
\texttt{right}, design a set of dedicated tactics for the interactive building of a battle.
Your tactics will have the following functionalities:
\begin{itemize}
\item  Choose to stop a battle, or continue
\item Choose an expected number of replications
\item Navigate in a hydra, looking for a head to chop off.
\end{itemize}

@@

The most general class of battles is \texttt{free}, which allows the hydra to choose any replication factor at every step:
